---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# `R`/MOSS

[![Travis-CI Build Status](https://travis-ci.org/wilsoncai1992/MOSS.svg?branch=master)](https://travis-ci.org/wilsoncai1992/MOSS)
[![Appveyor Build Status](https://ci.appveyor.com/api/projects/status/hagh8vidrdeacr7f?svg=true)](https://ci.appveyor.com/project/wilsoncai1992/MOSS)
[![codecov](https://codecov.io/gh/wilsoncai1992/MOSS/branch/master/graph/badge.svg)](https://codecov.io/gh/wilsoncai1992/MOSS)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![License: GPL v2](https://img.shields.io/badge/License-GPL%20v2-blue.svg)](https://www.gnu.org/licenses/gpl-2.0)
<!-- [![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/MOSS)](http://cran.rstudio.com/web/packages/MOSS/index.html) -->
<!-- [![](http://cranlogs.r-pkg.org/badges/MOSS)](http://cran.rstudio.com/web/packages/MOSS/index.html) [![](http://cranlogs.r-pkg.org/badges/grand-total/MOSS)](http://cran.rstudio.com/web/packages/MOSS/index.html) -->

MOSS performs ensemble machine learning and Targeted Maximum Likelihood (TMLE) to estimate the counter-factual marginal survival functions, while non-parametrically adjusting for measured confounding. TMLE approach is employed to create a doubly robust and semi-parametrically efficient estimator. Simultaneous confidence bands of the entire curve is also available for inference. User can specify what kind of static intervention on treatment (exposure).

The following comparable methods are also included in the package for you to easily compare methods:
- Inverse censoring probability weighted (IPCW)
- Locally efficient one-step estimator (estimating equation methods)

```{r eval = FALSE}
install.packages('MOSS')
devtools::install_github('wilsoncai1992/MOSS')
```

## Documentation

* To see all available package documentation:

```{r eval = FALSE}
?MOSS
help(package = 'MOSS')
```

## Brief overview

### Data structure

The data input of all methods in the package should be an `R` `data.frame` in the following survival long data format:

```{r eval = FALSE}
#   ID W A T.tilde delta
# 1  1 0 0      95     1
# 2  2 1 1       1     0
# 3  3 0 0     215     1
# 4  4 1 1      15     1
# 5  5 0 0      73     1
# 6  6 0 0      15     1
```

### Steps of analysis

1. perform SuperLearner fit of the conditional survival function of failure event, conditional survival function of censoring event, propensity scores (`initial_sl_fit`)
2. perform TMLE adjustment of the conditional survival fit (`MOSS_hazard`)
3. simultaneous confidence band (`compute_simultaneous_ci`)


## Citation
To cite `MOSS` in publications, please use:
> Cai W, van der Laan MJ (2019+). *One-step TMLE for time-to-event outcomes.* Working paper.

## Funding

## Copyright
This software is distributed under the GPL-2 license.

## Community Guidelines
Feedback, bug reports (and fixes!), and feature requests are welcome; file issues or seek support [here](https://github.com/wilsoncai1992/MOSS/issues).